Understanding domestic abuse

### 2019-07-26 JeS_fields.tex
Neil edits to JeS fields

As PI, Mullett will be responsible for coordinating the research. He will also act as the data controller for this project. Mullett has attained level three vetting with West Midlands Police, allowing him more comprehensive access to original police records, and he has the appropriate experience coordinating large datasets within projects. He will act as supervisor to the early career researcher Anna Trendl, ensuring that she can continue to build upon the research capabilities she has already developed during her PhD. As a member of the Centre for Operational Policing Research (COPR), he will, in tandem with Prof Neil Stewart, liaise with West Midlands Police to ensure that the results are communicated back in the most effective and interpretable manner. This will maximise the impact that this research produces.

As Co-I, Stewart's responsibilities will be to aid in coordinating the research program. He will also meet regularly with the early career researcher Anna Trendl, providing insights and support. A major role will also be to coordinate the communication of the results within the broader context of the Centre for Operational Policing Research (COPR) activities. This coordination, and the possibility for links and collaboration with other COPR members or projects will provide unique added value to the research.

As Post-Doctoral researcher, Trendl will be responsible for performing the analyses upon the data, and leading the writing of the resulting papers. She will also be deeply involved with impact related activity. As an early career researcher, it is crucial that she be given the opportunity to expand her network, and attain these new skills. The demands of this project mean it is essential that this is a postdoctoral role, and that the individual has a strong track record in statistical analysis, with datasets such as the CSEW and WMP records.

@@

This research uses a variety of existing data sets, to help us better understand the patterns, characteristics, and consequences of domestic abuse victimisation. The research will help to identify underlying risk factors for potential domestic abuse victims, and indicators for the most violent domestic abuse incidents, such as domestic homicide. We will engage with a number of stakeholders (police, domestic abuse charities, government), and provide insights relevant to their specific role in reducing the prevalence and harm caused by domestic abuse.

@@

The primary ethical concerns in this project centre around data privacy and data security. In particular the data held in the West Midlands Police dataset is highly sensitive, and if it were to end up in the wrong hands could be particularly damaging for the individuals present in the data, as well as for the WMP force, and even the researchers. For this reason we have developed our data security approach in tandem with WMP to ensure that data is only ever held and transported securely, and that researchers hold only the minimum amount of information in order to perform the research. We will never link individuals across datasets, and our lab data plan is fully compliant with GDPR.

@@

One potential concern is the possibility of consuming police resources that are needed elsewhere. This is an ever present consideration within the Centre for Operational Policing Research. WMP have already outputted their data, and we have applied data cleaning to it ourselves. Therefore, we will make very minimal requests on police resources. Our primary cost upon staff time will be during feeding back our results to influence policy. There are structuers within the police force specifically designed for this, so by presenting our findings to those, we will actually increase WMP efficiency.

>>>>

As PI, Mullett will be responsible for coordinating the research. He will also act as the data controller for this project. Mullett has attained level three vetting with West Midlands Police, allowing him more comprehensive access to original police records, and he has the appropriate experience coordinating large datasets within projects. He will act as supervisor to the early career researcher Anna Trendl, ensuring that she can continue to build upon the research capabilities she has already developed during her PhD. As a member of the Centre for Operational Policing Research (COPR), he will, in tandem with Prof Neil Stewart, liaise with West Midlands Police to ensure that the results are communicated back in the most effective and interpretable manner. This will maximise the impact that this research produces. Mullett will contribute extensively to the research design and writing academic papers.

As Co-I, Stewart's responsibilities will be to aid in coordinating the research program. He will also meet regularly with the early career researcher Anna Trendl, providing insights and support---Stewart has extensive experience supervising postdoctoral researchers. A major role will also be to coordinate the communication of the results within the broader context of the Centre for Operational Policing Research (COPR) activities. This coordination, and the possibility for links and collaboration with other COPR members or projects will provide unique added value to the research. Stewart will contribute to the research design and writing academic papers.

As Post-Doctoral researcher, Trendl will be responsible for performing the analyses upon the data, and, as is the norm in psychology, leading the writing of the resulting papers. She will also be deeply involved with impact related activity. As an early career researcher, it is crucial that she be given the opportunity to expand her network, and attain these new skills. The demands of this project mean it is essential that this is a postdoctoral role, and that the individual has a strong track record in statistical analysis. Trendl already has extensive experience with the WMP records.

@@

This research uses a variety of existing data sets, to help us better understand the patterns, characteristics, and consequences of domestic abuse victimisation. The research will help to identify underlying risk factors for potential domestic abuse victims, and indicators for the most violent domestic abuse incidents, such as domestic homicide. We will engage with a number of stakeholders (police, domestic abuse charities, national and local government), and provide insights relevant to their specific role in reducing the prevalence and harm caused by domestic abuse.

@@

The primary ethical concerns in this project centre around data privacy and data security. In particular, both the Crime Survey for England and Wales (secure access, low-level geographic data) and  the West Midlands Police datasets are highly sensitive. If data were to end up in the wrong hands could be particularly damaging for the individuals present in the data, as well as for the WMP force, and even the researchers. For this reason we have developed our data security approach in tandem with WMP to ensure that data is only ever held and transported securely, and that researchers hold only the minimum amount of information in order to perform the research. We also meet all of the standards for data security for accessing the secure access version of the Crime Survey for England and Wales.

We will never link individuals across datasets, and our lab data plan is fully compliant with GDPR.

@@

One potential concern is the possibility of consuming police resources that are needed elsewhere. This is an ever present consideration within the Centre for Operational Policing Research. WMP have already outputted their data, and we have applied data cleaning to it ourselves. Therefore, we will make very minimal requests on police resources. Our primary cost upon staff time will be during feeding back our results to influence police operations and policy. There are structures within the police force specifically designed for this, so by presenting our findings to those, we will actually increase WMP efficiency.
